---
title: "Lab 00 - Hello IDS!"
author: "Henry Feng"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Assa", "Anson", 
           "Amy", "Henry"),
  github_username = c("mcgregors-garden", "hakahagla", "Anson830", 
                      "amyyao987", "Mewk1ng"), 
  colour = c("powderblue", "blue", "blue", 
             "blue", "blue"),
  hobby = c("Hopping", "Sleep", "Football", 
            "Yoga", "Rugby"),
  favourite_number = c(2, 7, 10, 9, 7)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The graph shows our username and our favorite numbers.

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Favorite number",
          title = "Something about us")
```

It allows me to name headings.

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

It is not a nice representation because it is very likely everyone has unique hobbies, hence making all the bars the same height, which is quite meaningless.
